Figures and tables for paper

### 2021-12-02 analysis/04_figs-tables.Rmd
Added import code specific to each subset of hypotheses

if (intercept == 1) {

@@

```{r}
# Read in interaction draws for contrasts

intib <- read_rds(
    here::here("analysis", "output", "posterior_draws", "interactions.rds")
  )
```

@@

```{r branding-contrasts}
# Pull the posterior draws for the organizations and compute contrasts

contrasts <- tibble(
  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty = oxfam - amnesty,
    oxfam_greenpeace = oxfam - greenpeace,
    red_cross_amnesty = red_cross - amnesty,
    red_cross_greenpeace = red_cross - greenpeace,
  )

@@

# Hypothesis 2a, Relationship with Host Government

@@

```{r crackdown-contrasts-a}
# Pull the posterior draws for government crackdown

# Reference Level = Friendly relationship with government

@@

# Hypothesis 2b, Organization and Relationship with Host Government

@@

```{r crackdown-contrasts-b}
# Pull the posterior draws for organization*government crackdown interaction

# Reference Level = Friendly relationship with government

contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = oxfam_criticized - amnesty_criticized,
    oxfam_greenpeace_criticized = oxfam_criticized - greenpeace_criticized,
    red_cross_amnesty_criticized = red_cross_criticized - amnesty_criticized,
    red_cross_greenpeace_criticized = red_cross_criticized - greenpeace_criticized,
    oxfam_amnesty_crackdown = oxfam_crackdown - amnesty_crackdown,
    oxfam_greenpeace_crackdown = oxfam_crackdown - greenpeace_crackdown,
    red_cross_amnesty_crackdown = red_cross_crackdown - amnesty_crackdown,
    red_cross_greenpeace_crackdown = red_cross_crackdown - greenpeace_crackdown
  )
# Plot the contrasts
contrasts_int %>%
  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

@@

# Hypothesis 3a, Issue Area

@@

```{r issue-contrasts-a}
# Pull the posterior draws for issue area

# Reference Level = Emergency Response

@@

# Hypothesis 3b, Relationship with Host Government and Issue Area

@@

```{r issue-contrasts-b}

# Pull the posterior draws for government crackdown*issue area interaction

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response

contrasts_int <- tibble(
  criticized_environment = intib %>% filter(i == 22) %>% select(Gamma) %>% pull(),
  criticized_humanrights = intib %>% filter(i == 23) %>% select(Gamma) %>% pull(),
  criticized_refugee = intib %>% filter(i == 24) %>% select(Gamma) %>% pull(),
  crackdown_environment = intib %>% filter(i == 25) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = intib %>% filter(i == 26) %>% select(Gamma) %>% pull(),
  crackdown_refugee = intib %>% filter(i == 27) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  criticized_refugee_environment = criticized_refugee - criticized_environment,
  criticized_refugee_humanrights = criticized_refugee - criticized_humanrights,
  crackdown_refugee_environment = crackdown_refugee - crackdown_environment,
  crackdown_refugee_humanrights = crackdown_refugee - crackdown_humanrights
)
# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_refugee_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

# Hypothesis 4a, Funding Sources

@@

```{r funding-contrasts-a}
# Pull the posterior draws for funding sources

# Reference Level = Funded primarily by many small private donations

@@

# Hypothesis 4b, Relationship with Host Government and Funding Sources

@@

```{r funding-contrasts-b}
# Pull the posterior draws for government crackdown*funding sources interaction

# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations

contrasts_int <- tibble(
  criticized_wealthydonors = intib %>% filter(i == 28) %>% select(Gamma) %>% pull(),
  criticized_grants = intib %>% filter(i == 29) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = intib %>% filter(i == 30) %>% select(Gamma) %>% pull(),
  crackdown_grants = intib %>% filter(i == 31) %>% select(Gamma) %>% pull(),
)
# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_wealthydonors:crackdown_grants, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

# Hypothesis 4c, Relationship with Host Government, Funding Sources, and Issue Area

@@

```{r funding-contrasts-c}
# Pull the posterior draws for issue area*government crackdown*funding sources interaction

# Reference Level = Funded primarily by many small private donations
# Reference Level = Friendly relationship with government

@@

# Hypothesis 5a, Organizational Practices

@@

```{r practices-contrasts-a}

# Pull the posterior draws for organizational practices

@@

# Hypothesis 5b, Relationship with Host Government, Organizational Practices

@@

```{r practices-contrasts-b}

# Pull the posterior draws for organizational practices*government crackdown interaction

# Reference Level = Friendly relationship with government

@@

# Hypothesis 5c, Relationship with Host Government, Organizational Practices, and Funding Sources

@@

```{r practices-contrasts-c}
# Pull the posterior draws for organizational practices*funding sources*government crackdown interaction

# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations
# All interactions include financial transparency

@@

# Save plot
ggsave(
  "contrasts_hypothesis05c.png",#
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

@@

# Hypothesis 5d, Relationship with Host Government, Organizational Practices, and Issue Area

@@

```{r practices-contrasts-d}

# Pull the posterior draws for organizational practices*issue area*government crackdown interaction

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# All interactions include financial transparency

contrasts_int <- tibble(
  fin_emergency_criticized = intib %>% filter(i == 48) %>% select(Gamma) %>% pull(),
  fin_emergency_crackdown = intib %>% filter(i == 49) %>% select(Gamma) %>% pull(),
  fin_environment_criticized = intib %>% filter(i == 50) %>% select(Gamma) %>% pull(),
  fin_environment_crackdown = intib %>% filter(i == 51) %>% select(Gamma) %>% pull(),
  fin_humanrights_criticized = intib %>% filter(i == 52) %>% select(Gamma) %>% pull(),
  fin_humanrights_crackdown = intib %>% filter(i == 53) %>% select(Gamma) %>% pull(),
  fin_refugee_criticized = intib %>% filter(i == 54) %>% select(Gamma) %>% pull(),
  fin_refugee_crackdown = intib %>% filter(i == 55) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_emergency_environment_criticized = fin_emergency_criticized - fin_environment_criticized,
  fin_emergency_humanrights_criticized = fin_emergency_criticized - fin_humanrights_criticized,
  fin_emergency_environment_crackdown = fin_emergency_crackdown - fin_environment_crackdown,
  fin_emergency_humanright_crackdown = fin_emergency_crackdown - fin_humanrights_crackdown,
  fin_refugee_environment_criticized = fin_refugee_criticized - fin_environment_criticized,
  fin_refugee_humanright_criticized = fin_refugee_criticized - fin_humanrights_criticized,
  fin_refugee_environment_crackdown = fin_refugee_crackdown - fin_environment_crackdown,
  fin_refugee_humanright_crackdown = fin_refugee_crackdown - fin_humanrights_crackdown

@@

# Save plot
ggsave(
  "contrasts_hypothesis05d.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

@@

# Hypothesis 5e, Relationship with Host Government, Organizational Practices, Issue Area, and Funding Sources

@@

```{r practices-contrasts-e}
# Pull the posterior draws for organizational practices*funding*issue area*government crackdown interaction

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# All interactions include small donors
# All interactions include financial transparency

contrasts_int <- tibble(
  fin_sd_emergency_criticized = intib %>% filter(i == 56) %>% select(Gamma) %>% pull(),
  fin_sd_emergency_crackdown = intib %>% filter(i == 57) %>% select(Gamma) %>% pull(),
  fin_sd_environment_criticized = intib %>% filter(i == 58) %>% select(Gamma) %>% pull(),
  fin_sd_environment_crackdown = intib %>% filter(i == 59) %>% select(Gamma) %>% pull(),
  fin_sd_humanrights_criticized = intib %>% filter(i == 60) %>% select(Gamma) %>% pull(),
  fin_sd_humanrights_crackdown = intib %>% filter(i == 61) %>% select(Gamma) %>% pull(),
  fin_sd_refugee_criticized = intib %>% filter(i == 62) %>% select(Gamma) %>% pull(),
  fin_sd_refugee_crackdown = intib %>% filter(i == 63) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_sd_emergency_environment_criticized = fin_sd_emergency_criticized - fin_sd_environment_criticized,
  fin_sd_emergency_humanrights_criticized = fin_sd_emergency_criticized - fin_sd_humanrights_criticized,
  fin_sd_emergency_environment_crackdown = fin_sd_emergency_crackdown - fin_sd_environment_crackdown,
  fin_sd_emergency_humanright_crackdown = fin_sd_emergency_crackdown - fin_sd_humanrights_crackdown,
  fin_sd_refugee_environment_criticized = fin_sd_refugee_criticized - fin_sd_environment_criticized,
  fin_sd_refugee_humanright_criticized = fin_sd_refugee_criticized - fin_sd_humanrights_criticized,
  fin_sd_refugee_environment_crackdown = fin_sd_refugee_crackdown - fin_sd_environment_crackdown,
  fin_sd_refugee_humanright_crackdown = fin_sd_refugee_crackdown - fin_sd_humanrights_crackdown

  )
# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_sd_emergency_environment_criticized:fin_sd_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05e.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

@@

# Hypothesis 5f, Organizational Practices

@@

```{r practices-contrasts-b}
# Pull the posterior draws for organizational practices

@@

# Save plot
ggsave(
  "contrasts_hypothesis05f.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

>>>>

if (intercept == 1 & interactions == 0) {

@@

```{r}
# Read in interaction draws for contrasts
intib <- read_rds(
    here::here("analysis", "output", "posterior_draws", "interactions.rds")
  )

# Storing intercept draws in a different tibble for easier use; emergency response, no financial transparency, no accountability, many private donors and friendly relationship with government are all reference levels for their respective groups, and thus are not found in the tibble.
dtib <- tibble(
  amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(i == 2) %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(i == 3) %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(i == 9) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull()
)
```

@@

```{r branding-contrasts}
# Pull the posterior draws for the organizations and compute contrasts
contrasts <- tibble(
  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty = oxfam - amnesty,
    oxfam_greenpeace = oxfam - greenpeace,
    red_cross_amnesty = red_cross - amnesty,
    red_cross_greenpeace = red_cross - greenpeace,
  )

@@

#### Hypothesis 2a, Relationship with Host Government

@@

```{r crackdown-contrasts-a}
# Pull the posterior draws for government crackdown
# Reference Level = Friendly relationship with government

@@

#### Hypothesis 2b, Organization and Relationship with Host Government

@@

```{r crackdown-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_2b.rds")

# Pull the posterior draws for organization*government crackdown interaction
# Reference Level = Friendly relationship with government

contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
    oxfam_greenpeace_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
    red_cross_amnesty_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
    red_cross_greenpeace_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
    oxfam_amnesty_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
    oxfam_greenpeace_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown),
    red_cross_amnesty_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
    red_cross_greenpeace_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

```{r crackdown-contrasts-b-alt}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_2b.rds")

# Pull the posterior draws for organization*government crackdown interaction
# Reference Level = Friendly relationship with government

contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized),
    oxfam_greenpeace_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized),
    red_cross_amnesty_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized),
    red_cross_greenpeace_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized),
    oxfam_amnesty_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown),
    oxfam_greenpeace_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown),
    red_cross_amnesty_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown),
    red_cross_greenpeace_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis02b_alt.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
 )
```

@@

#### Hypothesis 3a, Issue Area

@@

```{r issue-contrasts-a}
# Pull the posterior draws for issue area
# Reference Level = Emergency Response

@@

#### Hypothesis 3b, Relationship with Host Government and Issue Area

@@

```{r issue-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_3b.rds")

# Pull the posterior draws for government crackdown*issue area interaction
# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response

contrasts_int <- tibble(
  criticized_environment = intib %>% filter(i == 22) %>% select(Gamma) %>% pull(),
  criticized_humanrights = intib %>% filter(i == 23) %>% select(Gamma) %>% pull(),
  criticized_refugee = intib %>% filter(i == 24) %>% select(Gamma) %>% pull(),
  crackdown_environment = intib %>% filter(i == 25) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = intib %>% filter(i == 26) %>% select(Gamma) %>% pull(),
  crackdown_refugee = intib %>% filter(i == 27) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  criticized_refugee_environment = criticized_refugee - criticized_environment,
  criticized_refugee_humanrights = criticized_refugee - criticized_humanrights,
  crackdown_refugee_environment = crackdown_refugee - crackdown_environment,
  crackdown_refugee_humanrights = crackdown_refugee - crackdown_humanrights
)

# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_refugee_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

#### Hypothesis 4a, Funding Sources

@@

```{r funding-contrasts-a}
# Pull the posterior draws for funding sources
# Reference Level = Funded primarily by many small private donations

@@

#### Hypothesis 4b, Relationship with Host Government and Funding Sources

@@

```{r funding-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_4b.rds")

# Pull the posterior draws for government crackdown*funding sources interaction
# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations

contrasts_int <- tibble(
  criticized_wealthydonors = intib %>% filter(i == 28) %>% select(Gamma) %>% pull(),
  criticized_grants = intib %>% filter(i == 29) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = intib %>% filter(i == 30) %>% select(Gamma) %>% pull(),
  crackdown_grants = intib %>% filter(i == 31) %>% select(Gamma) %>% pull(),
)

# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_wealthydonors:crackdown_grants, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

#### Hypothesis 4c, Relationship with Host Government, Funding Sources, and Issue Area

@@

```{r funding-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_4c.rds")

# Pull the posterior draws for issue area*government crackdown*funding sources interaction
# Reference Level = Funded primarily by many small private donations
# Reference Level = Friendly relationship with government

@@

#### Hypothesis 5a, Organizational Practices

@@

```{r practices-contrasts-a}
# Pull the posterior draws for organizational practices

@@

#### Hypothesis 5b, Relationship with Host Government, Organizational Practices

@@

```{r practices-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5b.rds")

# Pull the posterior draws for organizational practices*government crackdown interaction
# Reference Level = Friendly relationship with government

@@

#### Hypothesis 5c, Relationship with Host Government, Organizational Practices, and Funding Sources

@@

```{r practices-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5c.rds")

# Pull the posterior draws for organizational practices*funding sources*government crackdown interaction
# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations
# All interactions include financial transparency

@@

# Save plot
ggsave(
  "contrasts_hypothesis05c.png",#
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

@@

#### Hypothesis 5d, Relationship with Host Government, Organizational Practices, and Issue Area

@@

```{r practices-contrasts-d}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5d.rds")

# Pull the posterior draws for organizational practices*issue area*government crackdown interaction
# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# All interactions include financial transparency

contrasts_int <- tibble(
  fin_emergency_criticized = intib %>% filter(i == 48) %>% select(Gamma) %>% pull(),
  fin_emergency_crackdown = intib %>% filter(i == 49) %>% select(Gamma) %>% pull(),
  fin_environment_criticized = intib %>% filter(i == 50) %>% select(Gamma) %>% pull(),
  fin_environment_crackdown = intib %>% filter(i == 51) %>% select(Gamma) %>% pull(),
  fin_humanrights_criticized = intib %>% filter(i == 52) %>% select(Gamma) %>% pull(),
  fin_humanrights_crackdown = intib %>% filter(i == 53) %>% select(Gamma) %>% pull(),
  fin_refugee_criticized = intib %>% filter(i == 54) %>% select(Gamma) %>% pull(),
  fin_refugee_crackdown = intib %>% filter(i == 55) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_emergency_environment_criticized = fin_emergency_criticized - fin_environment_criticized,
  fin_emergency_humanrights_criticized = fin_emergency_criticized - fin_humanrights_criticized,
  fin_emergency_environment_crackdown = fin_emergency_crackdown - fin_environment_crackdown,
  fin_emergency_humanright_crackdown = fin_emergency_crackdown - fin_humanrights_crackdown,
  fin_refugee_environment_criticized = fin_refugee_criticized - fin_environment_criticized,
  fin_refugee_humanright_criticized = fin_refugee_criticized - fin_humanrights_criticized,
  fin_refugee_environment_crackdown = fin_refugee_crackdown - fin_environment_crackdown,
  fin_refugee_humanright_crackdown = fin_refugee_crackdown - fin_humanrights_crackdown
)

@@

# Save plot
ggsave(
  "contrasts_hypothesis05d.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

@@

#### Hypothesis 5e, Relationship with Host Government, Organizational Practices, Issue Area, and Funding Sources

@@

```{r practices-contrasts-e}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5e.rds")

# Pull the posterior draws for organizational practices*funding*issue area*government crackdown interaction
# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# All interactions include small donors
# All interactions include financial transparency

contrasts_int <- tibble(
  fin_sd_emergency_criticized = intib %>% filter(i == 56) %>% select(Gamma) %>% pull(),
  fin_sd_emergency_crackdown = intib %>% filter(i == 57) %>% select(Gamma) %>% pull(),
  fin_sd_environment_criticized = intib %>% filter(i == 58) %>% select(Gamma) %>% pull(),
  fin_sd_environment_crackdown = intib %>% filter(i == 59) %>% select(Gamma) %>% pull(),
  fin_sd_humanrights_criticized = intib %>% filter(i == 60) %>% select(Gamma) %>% pull(),
  fin_sd_humanrights_crackdown = intib %>% filter(i == 61) %>% select(Gamma) %>% pull(),
  fin_sd_refugee_criticized = intib %>% filter(i == 62) %>% select(Gamma) %>% pull(),
  fin_sd_refugee_crackdown = intib %>% filter(i == 63) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_sd_emergency_environment_criticized = fin_sd_emergency_criticized - fin_sd_environment_criticized,
  fin_sd_emergency_humanrights_criticized = fin_sd_emergency_criticized - fin_sd_humanrights_criticized,
  fin_sd_emergency_environment_crackdown = fin_sd_emergency_crackdown - fin_sd_environment_crackdown,
  fin_sd_emergency_humanright_crackdown = fin_sd_emergency_crackdown - fin_sd_humanrights_crackdown,
  fin_sd_refugee_environment_criticized = fin_sd_refugee_criticized - fin_sd_environment_criticized,
  fin_sd_refugee_humanright_criticized = fin_sd_refugee_criticized - fin_sd_humanrights_criticized,
  fin_sd_refugee_environment_crackdown = fin_sd_refugee_crackdown - fin_sd_environment_crackdown,
  fin_sd_refugee_humanright_crackdown = fin_sd_refugee_crackdown - fin_sd_humanrights_crackdown
)

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_sd_emergency_environment_criticized:fin_sd_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05e.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

@@

#### Hypothesis 5f, Organizational Practices

@@

```{r practices-contrasts-b}
# Pull the posterior draws for organizational practices
contrasts <- tibble(
  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
)

@@

# Save plot
ggsave(
  "contrasts_hypothesis05f.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```
